\plaintitle

### 2016-09-21 drafts/labor/discussion.tex
changes on subsections in discussion

\subsection{Polarizing Tendencies}\label{sec:polarizationOfCrowdWork}
\begin{enumerate}
  \item It's easy to think crowd work as heading toward some extreme
  \item Activists describe speculative workers as having
        ``essentially been turned into modern--day slaves''
        \cite{activistsHuffPoLawsuit}.
  \item Meanwhile, advocates describe it as
        ``a project of sharing
        aimed at providing ordinary people
        with more economic opportunities and
        improving their lives\dots''
        \cite{uberPropaganda}.
  \item There may be truth buried in both claims, but the important takeaway is that
        the closest we can get to a single truth is somewhere in the middled,
        buried in nuance.
  \item There may be a Utopian world at the end of the tunnel that is our world now:
        all work that we engage in could become speculative and risky;
        the layers between us and our managers might increasingly become
        ``defective (simple, observable)'' algorithms \cite{10.2307/2555446}
        --- the same ones which already seem to frustrate
        on--demand workers on Uber and other markets for labor
        \cite{uberAlgorithm,dynamo,turkopticon}.
  \item On the other hand, the future of crowd work could be eminently promising:
        piecework's nascent years were nothing short of grim, but
        they precipitated a century of the strongest labor advocacy the world has ever seen.
        In India, workers across the nation engaged in
        the largest labor strike in human history
        % \cite{indiaStrikeIndustriall,indiaStrikeAlJazeera}
        --- perhaps as many as 150 million
        \cite{indiaStrikeRealNews}.
        Arguably the Internet has made collective action on an unprecedented scale much easier.
  \item So are we heading toward \textit{Mad Max} or\dots
        \ali{is there a Utopian future movie?}
        If we do nothing, probably somewhere in the middle.
        It's possible that the difficulties of enforcing laws on multinational corporations is
        tipping the balance of power in the direction of corporations, in which case
        things will get worse;
        but arguably we can affect change on the trajectory of crowd work,
        benefiting from everything piecework scholars have learned about
        collective action and governance
        among workers, while also avoiding some of the perils they faced.
\end{enumerate}

>>>>

\subsection{Polarizing Tendencies}\label{sec:polarizationOfCrowdWork}
\topic{It would be easy
to think about the future of crowd work and
end up at one of two extremes.}
On one hand, crowd work researchers
imagine the application of crowdsourcing as
a potentially bright future that enables the achievement of near--impossible goals
\cite{redballoon,crowdworkFuture,vizwiz}; % \ali{and who else should I cite here?}
on the other hand, researchers
warn against crowd work as potentially exploitative sites of dispossession \cite{scholz2012digital},
a site of racial discrimination \cite{edelman2015racial},
and invisible, deeply frustrated workers \cite{turkopticon,bighamHalfWorkday}.

\topic{A uniquely challenging facet of this topic of inquiry is the public attention that this domain has attracted.}
Activists have described speculative work as having
``essentially been turned into modern--day slaves''
\cite{activistsHuffPoLawsuit}.
Meanwhile, advocates describe it as
``a project of sharing
aimed at providing ordinary people
with more economic opportunities and
improving their lives\dots''
\cite{uberPropaganda}.
\ali{these are salient, but with the last paragraph it feels really flimsy.
I'd really like to get this Uber quote in, but
not if it means this paragraph gets that much weaker.}

% \topic{There is, of course, a kernel of truth in everything here.}
\topic{There is evidence to support the claim that
a Dystopian world awaits us at the end of the tunnel.}
The arbitrary nature of on--demand work may permeate our lives, inducing us
``to neglect tasks that are less easy to measure'' \cite{SJOE:SJOE371}
rewarding us not for creativity but predictability;
payment for this work may ultimately be determined by
an algorithm that fundamentally doesn't understand us;
the layers between us and our managers might increasingly become
``defective (simple, observable)'' algorithms \cite{10.2307/2555446},
just like those which already frustrate
on--demand workers
\cite{uberAlgorithm,dynamo,turkopticon}.

\topic{On the other hand, there is some evidence that offers hope.}
Yes, piecework's nascent years were arguably grim, but
they precipitated a century of the strongest labor advocacy the world has ever seen
\cite{hart2013rise,mccallum2013global}.
Even today, the geist that came out of the labor union revolution
inspires collective action and worker empowerment around the world:
in India, workers across the nation engaged in
the largest labor strike in human history
--- perhaps as many as 150 million
\cite{indiaStrikeRealNews}.
If labor advocacy groups can find ways to permeate on--demand labor markets,
as some have called for
\cite{futureUnions},
then the future of crowd work may follow
the same trajectory of worker empowerment that piecework \textit{later} found.
\ali{The Internet may make this possible!}
% Arguably the Internet has made collective action on an unprecedented scale much easier.

\topic{Perhaps the most pressing question is this:
is the future of crowd work going to look more \textit{Dystopian} or \textit{Utopian}?}
% The unsatisfying answer is that
If we have learn nothing, crowd work will probably end up somewhere in the middle.
% It's possible that the difficulties of enforcing laws on multinational corporations is
% tipping the balance of power in the direction of corporations, in which case
% things will get worse;
% but arguably we can affect change on the trajectory of crowd work,
% benefiting from everything piecework scholars have learned about
% collective action and governance
% among workers, while also avoiding some of the perils they faced.
